Study locations

### 2022-11-02 Scripts/Map_study_locations.Rmd
Jauke dataset

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(gtools) #Library that allows to sort files by numerical order
library(tidyverse)
library(sf)
#Read all files with their paths
files <- dir("../Data/Clean_data", pattern="*.RData", full.names=T)
files <- mixedsort(files)

@@

#Read all file names
file_names <- dir("../Data/Clean_data", pattern="*.RData", full.names=F)
file_names <- mixedsort(file_names)

#Delete extension
file_names = str_replace(file_names, ".RData", "")
#Rename all elements of the list
names(all_data) <- file_names

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(gtools) #Library that allows to sort files by numerical order
library(tidyverse)
library(sf)
#Read all files with their paths
files <- dir("../Data/Clean_data", pattern="*.rds", full.names=T)
files <- mixedsort(files)

@@

#Read all file names
file_names <- dir("../Data/Clean_data", pattern="*.rds", full.names=F)
file_names <- mixedsort(file_names)

#Delete extension
file_names = str_replace(file_names, ".rds", "")
#Rename all elements of the list
names(all_data) <- file_names
